\documentclass[letterpaper,12pt]{article}

\usepackage[margin=.5in]{geometry}

\begin{document}

\noindent Joshua Matthews \& Kaitlin Poskaitis

\noindent Systems Programming

\noindent String Tokenizer

\section*{Design}
\subsection*{Duplicates}
Attempting to insert a duplicate into the list will not cause an error, but only
one copy of an item will be allowed in the list at any given time.

\subsection*{Data Ownership}
The void *s contained in the nodes are assumed to belong to the caller.
Therefore, if memory is malloced for these, it is the caller's job to free the
data.

\section*{Efficiency}
\subsection*{SLCreate}
This is O(1) as we just malloc the struct and set the compare function.

\subsection*{SLInsert}
This is O(n) because we start at the head of the list and iterate through until
we find the right spot. If the node is to be inserted at the end, then we need
to traverse the entire list.

\subsection*{SLRemove}
This is also O(n) because we start at the head and traverse the list until we
find the element to delete or have gone farther than the element can be. At
worst, the element is smaller than our smallest item, so the entire list gets
traversed.

\subsection*{SLDestroy}
This is also O(n) as we must free every node in the list.

\subsection*{SLCreateIterator}
This is O(1) because we malloc the struct and set its initial values in constant
time.

\subsection*{SLDestroyIterator}
This is O(n) because in the worst case you deleted the entire list but the
iterator is still pointing to the head, so you need to destroy all of the
following nodes.

\subsection*{SlNextItem}
This is at worst O(n) because if the node you are looking at got deleted, you go
back to the head and find where you should be, so you may iterate through the
whole list to get there.

\subsection*{IncNodeRef}
This is O(1) since we are incrementing a single value.

\subsection*{DecNodeRef}
This is O(n) because in the worst case the node you are looking at goes to 0 and
gets freed, as well as everything after it if the entire list was removed.

\subsection*{SlDestroyNode}
This is O(1) because it frees the memory that the node was in.

\end{document}
